### 2021-01-08 msc-thesis.tex
new diagrams
change Diagrams

Hier eine grobe Beschreibung des Basis Anwendungsfalls aufgeteilt in mehrere Bilder.

\includegraphics[width=15cm]{Selection Administrative Service.png}

\includegraphics[width=15cm]{Institution Determination.png}

\includegraphics[width=15cm]{Notify Institution.png}

\includegraphics[width=15cm]{Institution Request.png}

\includegraphics[width=15cm]{Submit Result.png}

@@

\includegraphics[width=15cm]{Sequence Diagram.png}

@@

\includegraphics[width=15cm]{Data Model.png}

>>>>

@@

\includegraphics[width=15cm]{Diagrams/out/Sequence Diagram/Sequence Diagram.png}

@@

\includegraphics[width=15cm]{Diagrams/out/Class Diagram/Class Diagram.png}
